Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/appendix.tex
Cosmetic Changes.
Work on text describing numerical results.

Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.

@@

We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.

>>>>

Another positivity-preserving IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclarren_etal_2008}).  
This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \quad \tilde{a}_{32} = 1, \nonumber \\
  a_{22} &= 0.5, \quad a_{33} = 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.

@@

We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \quad \tilde{a}_{32} = 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/imex.tex
Generalized the diffusion accurate requirement.
Added the plots for sine wave diffusion test.
Work on text describing numerical results.

To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
\begin{equation}
  \vect{u}^{(i)}
  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
  \label{eq:imexStagesRewrite}
\end{equation}
where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$.
(In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
Two types of IMEX schemes are considered: \emph{type A} and \emph{type ARS}.  
For IMEX schemes of type A, the matrix $A$ is invertible.  
For IMEX schemes of type ARS, the matrix $A$ can be written as
\[\left( 
   \begin{matrix} 
       0 & 0 \\ 
       0 & \hat{A}
   \end{matrix}
\right)\]
with $\hat{A}$ be invertible.
For $i=1,\ldots,s$, the coefficients
\begin{align*}
  c_{i0}
  =&\left\{
  \begin{array}{cl}
    1 - \sum_{j=1}^{i-1}c_{ij}  & \text{for type $A$,} \\
    1 - \sum_{j=2}^{i-1}c_{ij}  & \text{for type $ARS$;}
  \end{array}
  \right.\\
  \tilde{c}_{i0}
  =&\left\{
  \begin{array}{cl}
    0  & \text{for type $A$,} \\
   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
  \end{array}
  \right.\\
  c_{i1}
    =&\left\{
    \begin{array}{cl}
      \sum_{l =1}^{i-1} a_{il}b_{l1} & \text{for type $A$,} \\
      0  & \text{for type $ARS$;}
    \end{array}
    \right.\\
    \tilde{c}_{i1}
    =&\left\{
      \begin{array}{cl}
       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
       0  & \text{for type $ARS$;}
      \end{array}
      \right.
\end{align*}
and the rest coefficients were defined as in \cite{hu_etal_2017}.
For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
For type ARS schemes, the positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.)

@@

We therefore proceed to design GSA positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
To this end we define the vectors $\vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}$ and $\vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}$.  
In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.  
For the final stage ($i=s$), 
\begin{equation}
  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
\end{equation}
where $\vect{e}_{s}=(0,\ldots,0,1)^{T}$ and $\vect{e}=(1,\ldots,1)^{T}$.  
Thus, for $\vect{\cH}^{(s)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
\begin{equation}
  \vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e} = 1.
  \label{eq:diffusionCondition}
\end{equation}
Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.  
(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?  Does the answer to this depend on $s$?})
(We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators.)
To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
Instead, we only require the scheme to be second-order accurate in the streaming limit ($\vect{\cQ}=0$).  
This gives the order conditions
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}=1
  \quad\text{and}\quad
  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2}.  
  \label{eq:orderConditionsEx}
\end{equation}
We then seek to design GSA IMEX schemes with the following properties
\begin{itemize}
  \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
  \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
  \item Positivity-preserving (conditions given by \cite{hu_etal_2017}; with $c_{\mbox{\tiny Sch}}$ maximal).
  \item Few ($\le3$) implicit stages.
\end{itemize}
Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example of type ARS with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD).  
In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
It is also very similar to the scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclareen_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).  
In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.

>>>>

To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
\begin{equation}
  \vect{u}^{(i)}
  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
  \label{eq:imexStagesRewrite}
\end{equation}
where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$.
(In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
Two types of IMEX schemes are considered: \emph{type A} and \emph{type ARS}.  
For IMEX schemes of type A, the matrix $A$ is invertible.  
For IMEX schemes of type ARS, the matrix $A$ can be written as
\[\left( 
   \begin{matrix} 
       0 & 0 \\ 
       0 & \hat{A}
   \end{matrix}
\right)\]
with $\hat{A}$ be invertible.
For $i=1,\ldots,s$, the coefficients
\begin{align*}
  c_{i0}
  =&\left\{
  \begin{array}{cl}
    1 - \sum_{j=1}^{i-1}c_{ij}  & \qquad \text{for type $A$,} \\
    1 - \sum_{j=2}^{i-1}c_{ij}  & \qquad \text{for type $ARS$;}
  \end{array}
  \right.\\
  \tilde{c}_{i0}
  =&\left\{
  \begin{array}{cl}
    0  & \text{for type $A$,} \\
   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
  \end{array}
  \right.\\
  c_{i1}
    =&\left\{
    \begin{array}{cl}
      \sum_{l =1}^{i-1} a_{il}b_{l1} & \qquad ~\text{for type $A$,} \\
      \qquad ~ 0  & \qquad ~\text{for type $ARS$;}
    \end{array}
    \right.\\
    \tilde{c}_{i1}
    =&\left\{
      \begin{array}{cl}
       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
       0  & \text{for type $ARS$;}
      \end{array}
      \right.
\end{align*}
and the rest coefficients were defined as in \cite{hu_etal_2017}.
For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
For type ARS schemes, the positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.)

@@

We therefore proceed to design GSA positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
To this end we define the vectors $\vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}$ and $\vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}$.  
In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.  
Define
\begin{align*}
    \mathcal{A}^{-1}
    =&\left\{
      \begin{array}{cl}
       A^{-1} & \text{for type $A$,} \vspace{4pt} \\ 
       \left( 
          \begin{matrix} 
              0 & 0 \\ 
              0 & \hat{A}^{-1}
          \end{matrix}
       \right)  & \text{for type $ARS$.}
      \end{array}
      \right.
\end{align*}
For the final stage ($i=s$), 
\begin{equation}
  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
\end{equation}
where $\vect{e}_{s}=(0,\ldots,0,1)^{T}$ and $\vect{e}=(1,\ldots,1)^{T}$.  
Thus, for $\vect{\cH}^{(s)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
\begin{equation}
  \vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e} = 1.
  \label{eq:diffusionCondition}
\end{equation}
Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.  
(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?  Does the answer to this depend on $s$?})
(We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators.)
To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
Instead, we only require the scheme to be second-order accurate in the streaming limit ($\vect{\cQ}=0$).  
This gives the order conditions
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}=1
  \quad\text{and}\quad
  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2}.  
  \label{eq:orderConditionsEx}
\end{equation}
We then seek to design GSA IMEX schemes with the following properties
\begin{itemize}
  \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
  \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
  \item Positivity-preserving (conditions given by \cite{hu_etal_2017}; with $c_{\mbox{\tiny Sch}}$ maximal).
  \item Few ($\le3$) implicit stages.
\end{itemize}
Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example of type ARS with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD).  
In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
It is also very similar to the scheme given in \cite{mcclarren_etal_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).  
In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added the plots for sine wave diffusion test.
Work on text describing numerical results.

To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
In all tests, we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).

@@

The first test involves the streaming part only, and does not include any collisions ($\sigma_{\Ab}=\sigma_{\Scatt}=0$).  
We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition be given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
  \label{eq:initialConditionStreaming}
\end{equation}
We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
We use polynomials of degree $k=2$ for the spatial discretization (third-order spatial accuracy), and set the time step as $\Delta t = $.  
We vary the number of elements from $??$ to $??$ and compute errors for various time stepping schemes.

\ee{Include figure of error versus number of elements for various schemes.}

\begin{figure}[h]
  \centering
    \includegraphics[width=\textwidth]{figures/SineWaveStreaming}
   \caption{Sine Wave Streaming}
  \label{fig:SineWaveStreaming}
\end{figure}

@@

>>>>

To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
In all tests, we use third order accurate spatial discretization (polynomials of degree $k=2$) and we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).  
We compare results obtained using IMEX schemes proposed here (PA2+ and PARSD) with IMEX schemes from Hu et al. \cite{hu_etal_2017} (PA2), McClarren et al. \cite{mcclarren_etal_2008} (PC2), Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332), and Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2).  
In the streaming test, we also include results obtained with second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001} in the comparison (SSPRK2 and SSPRK3, respectively).  
See \ref{app:butcherTables} for further details.  
The time step is set to $\dt=0.1\times\dx$.

When comparing the numerical results to analytic solutions, errors are computed in the $L^{1}$-error norm.  
We compare results either in the absolute error ($E_{\mbox{\tiny Abs}}^{1}$) or the relative error ($E_{\mbox{\tiny Rel}}^{1}$), defined for a scalar quantity $u_{h}$ (approximating $u$) as
\begin{equation}
  E_{\mbox{\tiny Abs}}^{1}[u_{h}](t)
  =\f{1}{|D|}\sum_{\bK\in\mathscr{T}}\int_{\bK}|u_{h}(\vect{x},t)-u(\vect{x},t)|\,d\vect{x}
  \label{eq:errorNormAbsolute}
\end{equation}
and
\begin{equation}
  E_{\mbox{\tiny Rel}}^{1}[u_{h}](t)
  =\f{1}{|D|}\sum_{\bK\in\mathscr{T}}\int_{\bK}|u_{h}(\vect{x},t)-u(\vect{x},t)|/|u(\vect{x},t)|\,d\vect{x},
  \label{eq:errorNormRelative}
\end{equation}
respectively.  
The integrals in Eqs.~\eqref{eq:errorNormAbsolute} and \eqref{eq:errorNormRelative} are computed with a $3$-point Gaussian quadrature.

@@

The first test involves the streaming part only, and does not include any collisions ($\sigma_{\Ab}=\sigma_{\Scatt}=0$).  
We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition be given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
  \label{eq:initialConditionStreaming}
\end{equation}
We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
We vary the number of elements ($N$) from $8$ to $128$ and compute errors for various time stepping schemes.

In Figure~\ref{fig:SineWaveStreaming}, the absolute error for the number density $E_{\mbox{\tiny Abs}}^{1}[\cJ_{h}](t=10)$ is plotted versus $N$ (see figure caption for details).  
Errors obtained with SSPRK3 are smallest and decrease as $N^{-3}$ (cf. bottom black dash-dot reference line), as expected for a scheme combining third-order accurate time stepping with third-order accurate spatial discretization.  
For all the other schemes, using second-order accurate explicit time stepping, the error decreases as $N^{-2}$.  
Among the second-order accurate methods, SSP2332 has the smallest error, followed by RKCB2.  
The error for the remaining schemes (including SSPRK2) are indistinguishable on the plot.  
\begin{figure}[h]
  \centering
    \includegraphics[width=\textwidth]{figures/SineWaveStreaming}
   \caption{Absolute error (cf. Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements $N$ for the streaming sine wave test.  Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (black), SSP2332 (green), and PARSD (light red circles).  Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
  \label{fig:SineWaveStreaming}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionN} &
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionG}
    \end{tabular}
   \caption{Sine Wave Diffusion}
  \label{fig:SineWaveDiffusion}
\end{figure}
